Applying Renormalization Group Theory to the Square Well Liquid

### 2014-03-19 papers/thesis-roth/project.tex

The free energy density for each iteration is given by
\[
  f_i(T,n) = f_{i-1}(T,n) + \delta f_i(T,n)\ .
\]

The total free energy density is obtained when one takes the
iterations to infinity and adds in the attractive component:
\[
  f(T,n) = \lim_{i \to \infty} f_i(T,n) + f_{att}(T,n)\ .
\]

The initial free energy density, $f_0$ depends on the liquid model of study. For this work, I use the square well model:
\[
  f_0(T,n) = f_{id}(T,n) + f_{HS}(T,n) + a_2^{SW}(T,n)\ ,
\]
where $a_2^{SW}(T,n)$ is the second-order term in a high-temperature expansion around $1/\kt$.~\cite{Gil-Villegas97}

\subsection{Coexistence Curve Algorithm}
Coexistence curves are found by modifying the chemical potential $\mu$
in the grand free energy per volume $\Phi/V$. Grand free energy
density is defined as
\begin{align*}
  \frac{\Phi}{V} &= \phi \\
                 &= f(T,n) - n\mu \\
                 &= f(T,n) - n\frac{d}{dn}f(T,\npart)\ .
\end{align*}
It is the value $\npart$ that we adjust to find coexistence curves.

>>>>

The free energy density for each iteration is given by
\begin{equation}
  f_i(T,n) = f_{i-1}(T,n) + \delta f_i(T,n)\ .
\end{equation}
The total free energy density is obtained when one takes the
iterations to infinity and adds in the attractive component:
\begin{equation}
  f(T,n) = \lim_{i \to \infty} f_i(T,n) + f_{att}(T,n)\ .
\end{equation}
The initial free energy density, $f_0$ depends on the liquid model of study. For this work, I use the square well model:
\begin{equation}
  f_0(T,n) = f_{id}(T,n) + f_{HS}(T,n) + a_2^{SW}(T,n)\ ,
\end{equation}
where $a_2^{SW}(T,n)$ is the second-order term in a high-temperature expansion around $1/\kt$.~\cite{Gil-Villegas97}

\subsection{Coexistence Curve Algorithm}
Coexistence curves are found by modifying the chemical potential $\mu$
in the grand free energy per volume $\Phi/V$. Grand free energy
density is defined as
\begin{align}
  \frac{\Phi}{V} &= \phi \nonumber \\
                 &= f(T,n) - n\mu \nonumber \\
                 &= f(T,n) - n\frac{d}{dn}f(T,\npart)\ .
\end{align}
It is the value $\npart$ that we adjust to find coexistence curves.
